\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-12-04 docs/paper/paper.tex
Changed paragraph spacing and document type.

% Needed packages
\documentclass[a4paper, 10pt, english, twocolumn]{article}
\usepackage[english]{babel}
\usepackage[cm]{fullpage}
\usepackage{cite}
\usepackage{anysize}
\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{listings}
\usepackage{hyperref}

@@

@@

% Explicit test
A more direct way to decrease faulty orientation of an unshielded triple $\left<A,B,C\right>$ is to check whether adding $B$ to a separating set of $(A,C)$ makes the pair conditionally dependent.
If so, the graph is likely to be more faithful to its modeled distribution.

\paragraph{EMS PC}
...

>>>>

% Needed packages
\documentclass[a4paper, 10pt, english, onecolumn]{article}
\usepackage[english]{babel}
\usepackage[cm]{fullpage}
\usepackage{cite}
\usepackage{anysize}
\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{listings}
\usepackage{hyperref}

@@

\setlength{\parindent}{0.0cm}
\setlength{\parskip}{0.25cm}

@@

% Explicit test
A more explicit way to decrease faulty orientation of an unshielded triple $\left<A,B,C\right>$ is to check whether adding $B$ to a separating set of $(A,C)$ makes the pair conditionally dependent.
If so, the graph is likely to be more faithful to its modeled distribution.

\paragraph{EMS-PC}
We have combined the above ideas into an adaptation of PC, which we refer to as Explicit Multiple Separating Set PC (EMS-PC).
% TODO: Algorithmic part here.
